Analysis of Toronto Homeless Shelter System

### 2023-01-27 outputs/paper/paper.qmd
Code from Practice.qmd

---
title: "Analysis of Toronto Homeless Shelter"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
bibliography: references.bib
---

@@

>>>>

---
title: "Analysis of Toronto Homeless Shelter System"
subtitle: "My subtitle if needed"
author: "Huda Sahaf"
thanks: "Code and data are available at: https://open.toronto.ca/catalogue/."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
bibliography: references.bib
---

```{r}
library(tidyverse)
library(janitor)
library(dplyr)
library(ggplot2)
library(opendatatoronto)
```

```{r}
###Read in Data####
raw_shelter_data<-
  read_csv(
    file = 
      "https://ckan0.cf.opendata.inter.prod-toronto.ca/dataset/ac77f532-f18b-427c-905c-4ae87ce69c93/resource/237d5eff-ba47-46c4-8717-a92a802abdf7/download/toronto-shelter-system-flow.csv",
    show_col_types = FALSE
  )
write_csv(
  x = raw_shelter_data,
  file = "to_shelter_system.csv"
)
head(raw_shelter_data)
tail(raw_shelter_data)
```

```{r}
####Basic Cleaning ###
raw_shelter_data<-
  read_csv(
    file = "to_shelter_system.csv",
    show_col_types = FALSE
  )
# Make the names easier to type
cleaned_shelter_data <-
  clean_names(raw_shelter_data)

# Have a look at the first six rows
head(cleaned_shelter_data)
```

```{r}
#### Renaming the columns ####
names(cleaned_shelter_data)

cleaned_shelter_data<-
  cleaned_shelter_data |>
  rename(
    dates = date_mmm_yy,
    group_percentage = population_group_percentage,
    trans_nb_twospirit = gender_transgender_non_binary_or_two_spirit,
    male = gender_male,
    female = gender_female,
    over65 = age65over,
    under16 = ageunder16
  )
head(cleaned_shelter_data)
```

```{r}
#### Simplifying the Dates: #### 
cleaned_shelter_data <-
  cleaned_shelter_data |>
  separate(
    col = dates,
    into = c("Month", "Year"),
    sep = "-"
  )
head(cleaned_shelter_data)
```

@@

```{r}
?tibble
```
